Convective penetration probably parameterizes convective overshoot

### 2021-07-14 manuscript/ms.tex
incorporates (I think?) all suggestions from Daniel; cleans up a few rough edges.

The mechanisms referred to as ``convective overshoot'' in the stellar literature fall into two hydrodynamical classes.
The first class is confusingly also called ``\emph{convective overshoot}'' in the fluid dynamics literature, and refers to motions which extend beyond the convective boundary but do not adjust the thermodynamic profiles.
The second class is called ``\emph{convective penetration},'' and refers to convective motions which mix the thermodynamic profiles beyond the convective boundary, thereby extending the adiabatically-mixed convective region.
We will follow a deep history \citep{zahn1991, brummell_etal_2002, korre_etal_2019} and use this terminology; the primary focus of this work is convective penetration.
We are interested in the case where there are no composition gradients, and where the flux driving the convection is constant over long timescales.
We are therefore not focused on the mechanisms by which convection zones grow \citep[e.g., entrainment, ][]{meakin_arnett_2007, viallet_etal_2013, cristini_etal_2017, fuentes_cumming_2020, horst_etal_2021}, but rather the extent of saturated, statistically-stationary convective regions.

Convective overshoot, penetration, and entrainment have been studied in the laboratory and through numerical simulations for decades, and the state of the field has been regularly reviewed \citep[e.g.,][]{marcus_etal_1983, zahn1991, browning_etal_2004, rogers_etal_2006, viallet_etal_2015, korre_etal_2019}.
Modern numerical experiments often examine the importance of the ``stiffness'' of a radiative-convective interface.
The stiffness measures the relative stability of a radiative zone and an adjacent convection zone according to some measure like a dynamical frequency or characteristic entropy gradient.
Experiments exhibiting extensive expansion of convection zones via entrainment have a long history \citep[dating back to e.g.,][and this process is often confusingly called ``penetration'']{musman1968, deardorff_etal_1969, moore_weiss_1973}.
Some recent studies in simplified Boussinesq setups exhibit stiffness-dependent convection zone expansion via entrainment \citep{couston_etal_2017, toppaladoddi_wettlaufer_2018}; others find stiffness-dependent overshoot \citep{korre_etal_2019}.
While a clear link between stiffness and entrainment and overshoot has seemingly emerged in these simple simulation setups, a clear mechanism for penetration remains elusive.

Studies which more closely model the conditions inside of stars have presented confusing results.
Many studies have exhibited hints of penetrative convection -- that is, mixing of the entropy gradient towards the adiabatic beyond the convective boundary \citep{hurlburt_etal_1986, hurlburt_etal_1994, singh_etal_1995, saikia_etal_2000, browning_etal_2004, rogers_etal_2006, kitiashvili_etal_2016, brun_etal_2017, pratt_etal_2017, higl_etal_2021}.
These simulations include simple plane-parallel studies of compressible convection as well as global 3D simulations which employ profiles from stellar structure codes as background states.
However, fundamental studies in both Cartesian and spherical geometries have exhibited little to no dependence of penetration on the stiffness \citep{brummell_etal_2002, rogers_glatzmaier_2005}.
This host of experiments suggests that convective penetration is \emph{probably} a process that happens in stars, but no clear model has emerged which explains whether convective penetration depends on stiffness or some other quantity.

@@

The Schwarzschild criterion for convective stability separates regions where convective motions are required to carry the flux from regions where radiation is capable of carrying the flux stably.
\emph{Convective penetration} is the process by which realistic convective motions extend beyond the Schwarzschild-stable boundary and mix the entropy gradient towards the adiabatic.
\begin{quote}
\emph{
In this paper, we present simulations which consistently exhibit convective penetration.
}
\end{quote}
These simulations exhibit nearly adiabatic regions beyond the Schwarzschild boundaries of the convection zone.
This process is phenomenologically described in Sec.~\ref{sec:central_results}.

In order to understand this phenomenon, we derive theoretical predictions for the size of the penetrative zone based on the ideas of \citet{roxburgh1989} and \citet{zahn1991}.
We design and carry out numerical experiments to test the idea that the penetration depth depends on the shape of the radiative gradient at the convective boundary.
\begin{quote}
\emph{
We find that the extent of convective penetration depends strongly on the shape and magnitude of the radiative gradient near the convective boundary.
}
\end{quote}
Thus, the penetration depth can be calculated using the radiative conductivity (or opacity) \emph{profile} near the convective boundary.

We present these findings as follows.
In Sec.~\ref{sec:central_results}, we note the central results of this work.
In Sec.~\ref{sec:theory}, we describe our modified Boussinesq equations, derive a theory of convective penetration, and derive predictions for our two experimental designs from that theory.
In Sec.~\ref{sec:simulation_details}, we describe our simulation setup and parameters.
In Sec.~\ref{sec:results}, we present the results of these simulations, with a particular focus on the depth of the penetrative regions.
In Sec.~\ref{sec:solar_model}, we create and discuss a solar MESA model which uses this theory to determine the bottom of the solar convection zone.
Finally, we discuss how future simulations can better constrain this theory in Sec.~\ref{sec:discussion}.

@@

\section{Central Results}
\label{sec:central_results}

In Fig.~\ref{fig:vertical_dynamics_panels}, we display a snapshot of dynamics in an evolved simulation which exhibits convective penetration.
The simulation domain is a 3D Cartesian box, and this figure shows a vertical slice through the center of the domain.
In the left panel, we display the vertical velocity.
We see that convective motions extend beyond the Schwarzschild boundary of the convection zone, which is denoted by a horizontal dashed grey line.
These motions come to a halt at the top of a penetration zone, denoted by a solid horizontal line, where the gradient departs from the adiabatic towards the radiative gradient.
In the right panel, we display temperature perturbations from the time-evolving mean temperature profile, normalized by the standard deviation of these fluctuations at each height.
We see that warm upwellings in the Schwarzschild-unstable convection zone (below the dashed line) become cold upwellings in the penetration zone (above the dashed line), and these motions excite gravity waves in the stable radiative zone (above the solid line).

In Fig.~\ref{fig:grad_profiles}, we display time- and horizontally-averaged 1D profiles of the thermodynamic gradient $\justgrad$ (defined in Sec.~\ref{sec:theory}).
The adiabatic gradient $\gradad$ is shown in purple and is a constant value in the simulation.
The radiative gradient $\gradrad$ is shown in orange.
The domain exhibits a classical Schwarzshild-unstable convection zone (CZ) for $z \lesssim 1.04$ where $\gradrad > \gradad$; the upper boundary of this region is denoted by a dashed vertical line.
Above this point, $\gradrad < \gradad$ and is Schwarzschild-stable.
However, the evolved convective dynamics in Fig.~\ref{fig:vertical_dynamics_panels} have flattened $\justgrad \rightarrow \gradad$ in an extended penetration zone (PZ) which extends from roughly $1.04 \leq z \leq 1.4$.
Above this point, $\justgrad$ departs from $\gradad$, returning to $\gradrad$ in a classical stable radiative zone (RZ).

Our goal in this paper is to understand how these PZs form, and to begin to understand how to parameterize this effect so that it can be included in 1D stellar evolution calculations.

\section{Theory}
\label{sec:theory}

\subsection{Equations \& flux definitions}
\label{sec:theory_equations}
Throughout this work, we will utilize a modified version of the incompressible Boussinesq equations of motion,
\begin{align}
&\grad\dot\vec{u} = 0 
\label{eqn:incompressible} \\
&\partial_t \vec{u} + \vec{u}\dot\grad\vec{u} = -\frac{1}{\rho_0}\grad p + \frac{\rho_1}{\rho_0}\vec{g} + \nu\grad^2 \vec{u} 
\label{eqn:momentum} \\
&\partial_t T + \vec{u}\dot\grad T + w \gradad + \grad\dot[-k \grad \overline{T}] = \chi\grad^2 T' + Q
\label{eqn:temperature} \\
&\frac{\rho_1}{\rho_0} = -|\alpha| T.
\label{eqn:boussinesq}
\end{align}
Here, the density is decomposed into a constant background $\rho_0$ with fluctuations $\rho_1$ which appear only in the buoyancy force and depend on the temperature $T$ and the coefficient of thermal expansion $\alpha = \partial\ln\rho / \partial T$.
We furthermore define the velocity vector $\vec{u}$, the viscous diffusivity $\nu$, the thermal diffusivity $\chi$, the bulk internal heating $Q$ \citep[similar but not identical to that described in e.g.,][]{goluskin2016}, the adiabatic gradient $\gradad$, and a height-dependent thermal conductivity $k$.
We will consider Cartesian coordinates $(x, y, z)$ with a constant vertical gravity $\vec{g} = -g\hat{z}$.
Throughout this work, we will represent horizontal averages with bars ($\overline{\,\cdot\,}$) and fluctuations away from those averages with primes ($'$).
Thus, in Eqn.~\ref{eqn:temperature}, $\bar{T}$ is the horizontally averaged temperature and $T'$ are fluctuations away from that; both of these fields evolve in time according to Eqn.~\ref{eqn:temperature}.

@@

Taking a dot product of the velocity and Eqn.~\ref{eqn:momentum} reveals the kinetic energy equation,
\begin{equation}
\frac{\partial \mathcal{K}}{\partial t}
+ \grad\dot\mathcal{F}
= \mathcal{B} - \Phi,
%\frac{\partial}{\partial t}\left(\frac{|\vec{u}|^2}{2}\right) 
%+ \grad\dot\left[\vec{u}\left(\frac{|\vec{u}|^2}{2} + \frac{p}{\rho_0}\right) - \nu\vec{u}\cross\vec{\omega}\right]
%= |\alpha| g w T - \nu|\vec{\omega}|^2,
\label{eqn:kinetic_energy}
\end{equation}
where we define the kinetic energy $\mathcal{K} \equiv |\vec{u}|^2/2$, the fluxes of kinetic energy $\mathcal{F} \equiv \left[\vec{u}(\mathcal{K} + p/\rho_0) - \nu\vec{u}\cross\vec{\omega} \right]$, the buoyant energy generation rate $\mathcal{B} \equiv |\alpha| g w T'$, and the viscous dissipation rate $\Phi \equiv \nu |\vec{\omega}|^2$ where $\vec{\omega} = \grad\cross\vec{u}$ is the vorticity and $|\vec{u}|^2 = \vec{u}\dot\vec{u}$ \& $|\vec{\omega}|^2 = \vec{\omega}\dot\vec{\omega}$.
We next take a horizontal- and time-average of Eqn.~\ref{eqn:kinetic_energy} (we absorb the time-average into the horizontal-average $\bar{\,\cdot\,}$ notation for simplicity).
Assuming that $\bar{\mathcal{K}}$ reaches a statistically stationary state, convective motions satisfy
\begin{equation}
\frac{d\bar{\mathcal{F}}}{dz} = \bar{\mathcal{B}} - \bar{\Phi}.
\label{eqn:kinetic_energy_1D}
\end{equation}
It is reasonable to assume that $\mathcal{F}$ is zero at the boundaries of the convecting region (see Fig.~\ref{fig:theory_profiles}, left panel).
We integrate Eqn.~\ref{eqn:kinetic_energy_1D} vertically between these zeros of the flux to find
\begin{equation}
\int \bar{\mathcal{B}}\,dz = \int \bar{\Phi}\,dz.
\label{eqn:integral_constraint}
\end{equation}
Integral constraints of this form are the basis for a broad range of analyses in Boussinesq convection \citep[see e.g.,][]{ahlers_etal_2009, goluskin2016} and were considered in the context of penetrative stellar convection by \citet{roxburgh1989}.
Eqn.~\ref{eqn:integral_constraint} is the straightforward statement that work by buoyancy on large scales must be balanced by viscous dissipation on small scales.

@@

We now find it instructive to break up the convecting region into a Schwarzschild-unstable ``convection zone'' (CZ) and a extended ``penetration zone'' (PZ); we assume that convective motions efficiently mix $\justgrad \rightarrow \gradad$ in both the CZ and PZ.
We note that the buoyant energy generation is proportional to the convective flux, $\bar{\mathcal{B}} = |\alpha|g\bar{w T'} = |\alpha| g \bar{\Fconv}$.
Thus, in the PZ where $\gradad > \gradrad$ (see Fig.~\ref{fig:theory_profiles}, middle panel), we know that $\bar{\Fconv} < 0$ and so $\bar{\mathcal{B}} < 0$ too (see the discussion around Eqn.~\ref{eqn:gradrad_definition}).
Breaking up Eqn.~\ref{eqn:integral_constraint}, we see that
\begin{equation}
%\int_{\rm{CZ}} \bar{\mathcal{B}}\,dz \qquad=\qquad
\int_{\rm{CZ}} \bar{\mathcal{B}}\,dz \,\,=\,\,
\int_{\rm{CZ}} \bar{\Phi}\,dz + \int_{\rm{PZ}} \bar{\Phi}\,dz + \int_{\rm{PZ}}(-\bar{\mathcal{B}})\,dz.
\label{eqn:constraint_cz_pz_split}
\end{equation}
Eqn.~\ref{eqn:constraint_cz_pz_split} is thus arranged so that the (positive) buoyant engine of convection is on the left-hand side, and the (positive) sinks of work are on the RHS.
We see that the size of the PZ is set by some combination of viscous dissipation and buoyancy breaking.
We now parameterize the fraction of the buoyant engine consumed by CZ dissipation  
\begin{equation}
f \equiv \frac{\int_{\rm{CZ}} \bar{\Phi}\,dz}{\int_{\rm{CZ}}\bar{\mathcal{B}}\,dz}.
\label{eqn:f_defn}
\end{equation}
Under this parameterization, Eqn.~\ref{eqn:constraint_cz_pz_split} can be written
\begin{equation}
\frac{\int_{\rm{PZ}} \bar{\Phi}\,dz }{\int_{\rm{CZ}} \bar{\mathcal{B}}\,dz}
+ \frac{\int_{\rm{PZ}}(-\bar{\mathcal{B}})\,dz}{\int_{\rm{CZ}} \bar{\mathcal{B}}\,dz}
= 1 - f,
\label{eqn:first_pz_parameterization}
\end{equation}
and we can immediately read off limits on a hypothetical PZ according to $f$,
\begin{enumerate}
\item Viscous dissipation is inefficient in the limit that $f \rightarrow 0$.
Reasonably also assuming that $\int_{\rm{PZ}}\bar{\Phi}\,dz \rightarrow 0$, Eqn.~\ref{eqn:first_pz_parameterization} states that the PZ must be large enough for its negative buoyant work to be equal in magnitude to the positive buoyant work of the CZ.
This is the integral constraint on the maximum size of the PZ that \citet{roxburgh1989} derived.
\item In the limit that $f \rightarrow 1$, viscous dissipation efficiently counteracts the buoyancy work in the CZ.
Per Eqn.~\ref{eqn:first_pz_parameterization}, the positive-definite PZ terms must approach zero and no PZ develops in this limit.
This is mathematically equivalent to standard boundary-driven convection experiments.
\end{enumerate}
In general, we anticipate from the results of e.g., \citet{currie_browning_2017} that $f$ is closer to 1 than 0, but its precise value must be measured directly from simulations.
Indeed, we find that $f \gg 0$ but $f < 1$ in our simulations (see e.g., Fig.~\ref{fig:theory_profiles}, right panel).

@@

The fundamental result of this theory is Eqn.~\ref{eqn:theory_fraction}, which is a parameterized and generalized form of \citet{roxburgh1989}'s integral constraint.
The parameters $f$ and $\xi$ are measurables which can be constrained by direct numerical simulations.
In general, we expect that $f$ and $\xi$ should not change too drastically with other simulation parameters.

@@

In Fig.~\ref{fig:time_evolution}, we show the time evolution of a Case I (discontinuous conductivity) simulation with $\mR = 400$, $\mS = 10^3$, and $\mP_D = 4$ whose initial conditions roughly set $\justgrad = \gradad$ in the convection zone ($z \lesssim 1$) and $\justgrad = \gradrad$ in the radiative zone ($z \gtrsim 1$).
In the top left panel, we display the measured extent of the penetrative region $\delta_{\rm{0.5}}$ vs.~time.
This region initially grows quickly over hundreds of freefall times, but this evolution slows down as the convective dynamics establish themselves and the final equilibration takes tens of thousands of convective overturn (freefall) times.
The evolution of the other parameters in our theory ($f$, $\xi$) are shown in the middle and bottom left panels of Fig.~\ref{fig:time_evolution}.
We plot their rolling mean, averaged over 200 freefall time units. 
We see that the values of $f$ and $\xi$ reach their final values ($f \approx 0.67$, $\xi \approx 0.58$) faster than the penetration zone evolves to its full depth.
We quantify this fast evolution by plotting a vertical line in each of the left three panels corresponding to the first time at which the rolling average converges to within 1\% of its final value (averaged over the final 1000 freefall times of the simulation and plotted as a grey horizontal line).
The evolved value of $f$ indicates that roughly 2/3 of the buoyancy work is dissipated in the bulk CZ, so that 1/3 is available for PZ dissipation negative buoyancy work.
The evolved value of $\xi$ indicates that the shape of dissipation in the PZ is slightly steeper than linear.

In the right panel of Fig.~\ref{fig:time_evolution}, we display the realized profile of $\justgrad/\gradad$ in our simulations at regular time intervals (where the color of the profiles corresponds to time, as in the left panels).
$\gradad$ is plotted as a dashed horizontal line while $\gradrad$ is plotted as a grey solid line which decreases with height around $z \approx 1$ and satures to a constant above $z \gtrsim 1.1$.
The location of the Schwarzschild boundary, $L_s$, is overplotted as a black vertical dashed line and does not evolve over the course of the simulation.
We note that the Schwarzschild boundary does not move over the course of our simulation, so the extention of the convection zone past this point is true penetration and not the result of entrainment-induced changes in the Schwarzschild (or Ledoux) convective boundaries.
The traces of $\delta_{0.1}$ and $\delta_{0.9}$ are plotted as red lines while that of $\delta_{0.5}$ is plotted as a black line.
We can see that the fast initial evolution establishes a sizeable PZ (denoted by purple $\justgrad$ profiles), but its final equilibration slows down (indicated by the separation between the purple, green, and yellow profiles decreasing over time).
This occurs in part because the flattening of $\justgrad < \gradrad$ above the penetrative zone increases the effective value of $N^2$ and thus the stiffness at the PZ-RZ boundary.

>>>>

The broad category of ``convective overshoot'' in the stellar literature is an umbrella term for a few hydrodynamical processes.
The first process is confusingly also called ``\emph{convective overshoot}'' in the fluid dynamics literature, and refers to motions which extend beyond the convective boundary but do not adjust the thermodynamic profiles.
The second process is called ``\emph{convective penetration},'' and refers to convective motions which mix the thermodynamic profiles beyond the convective boundary, thereby extending the adiabatically-mixed convective region.
We will follow a deep history \citep{zahn1991, brummell_etal_2002, korre_etal_2019} and use this terminology.
Many studies have also examined \emph{entrainment}, the process by which convection zones expand by eroding composition gradients or modifying the radiative gradient \citep[][]{meakin_arnett_2007, viallet_etal_2013, cristini_etal_2017, fuentes_cumming_2020, horst_etal_2021}.
The primary focus of this work is convective penetration.

Convective overshoot, penetration, and entrainment have been studied in the laboratory and through numerical simulations for decades, and the state of the field has been regularly reviewed \citep[e.g.,][]{marcus_etal_1983, zahn1991, browning_etal_2004, rogers_etal_2006, viallet_etal_2015, korre_etal_2019}.
Modern numerical experiments often examine the importance of the ``stiffness'' of a radiative-convective interface.
The stiffness measures the relative stability of a radiative zone and an adjacent convection zone according to some measure like a dynamical frequency or characteristic entropy gradient.
Experiments exhibiting extensive expansion of convection zones via entrainment have a long history \citep[dating back to e.g.,][and this process is often confusingly called ``penetration'']{musman1968, deardorff_etal_1969, moore_weiss_1973}.
Some recent studies in simplified Boussinesq setups exhibit stiffness-dependent convection zone expansion via entrainment \citep{couston_etal_2017, toppaladoddi_wettlaufer_2018}; others find stiffness-dependent pure overshoot \citep{korre_etal_2019}.
While a clear link between stiffness and entrainment and overshoot has seemingly emerged in these simple simulation setups, a clear mechanism for penetration remains elusive.

Studies which more closely model the conditions inside of stars have presented confusing results.
Many studies have exhibited hints of penetrative convection -- that is, mixing of the entropy gradient towards the adiabatic beyond the convective boundary \citep{hurlburt_etal_1986, hurlburt_etal_1994, singh_etal_1995, saikia_etal_2000, browning_etal_2004, rogers_etal_2006, kitiashvili_etal_2016, brun_etal_2017, pratt_etal_2017, higl_etal_2021}.
These simulations include simple plane-parallel studies of compressible convection as well as global 3D simulations which employ profiles from stellar structure codes as background states.
Unfortunately, other fundamental studies in both Cartesian and spherical geometries have exhibited little to no dependence of penetration on the stiffness \citep{brummell_etal_2002, rogers_glatzmaier_2005}.
This host of experiments suggests that convective penetration is \emph{probably} a process that happens in stars, but no clear model has emerged which explains whether convective penetration depends on stiffness or some other quantity.

@@

Convective penetration is the process by which realistic convective motions extend beyond the Schwarzschild-stable boundary and mix the entropy gradient towards the adiabatic.
\begin{quote}
\emph{
In this paper, we present simulations which exhibit convective penetration.
}
\end{quote}
This process is phenomenologically described in Sec.~\ref{sec:central_results}.

In order to understand this phenomenon, we derive theoretical predictions for the size of the penetrative zone based on the ideas of \citet{roxburgh1989} and \citet{zahn1991}.
%We design and carry out numerical experiments to test the idea that the penetration depth depends on the shape of the radiative gradient at the convective boundary.
\begin{quote}
\emph{
We find that the extent of convective penetration depends strongly on the shape and magnitude of the radiative gradient near the convective boundary.
}
\end{quote}
Thus, the penetration depth can be calculated using the radiative conductivity (or opacity) \emph{profile} near the convective boundary.

We present these findings as follows.
In Sec.~\ref{sec:central_results}, we present the central finding of this work: penetration zones in nonlinear convective simulations.
In Sec.~\ref{sec:theory}, we describe the equations used and derive a parameterized theory of convective penetration.
In Sec.~\ref{sec:simulation_details}, we describe our simulation setup and parameters.
In Sec.~\ref{sec:results}, we present the results of these simulations, with a particular focus on the depth of the penetrative regions.
In Sec.~\ref{sec:solar_model}, we create and discuss a solar MESA model which uses this theory to determine the bottom of the solar convection zone.
Finally, we discuss how future simulations can better constrain this theory in Sec.~\ref{sec:discussion}.

@@

\section{Central Result: Convective Penetration}
\label{sec:central_results}

In Fig.~\ref{fig:vertical_dynamics_panels}, we display a snapshot of dynamics in an evolved simulation which exhibits convective penetration.
The simulation domain is a 3D Cartesian box, and this figure shows a vertical slice through the center of the domain.
In the left panel, we display the vertical velocity.
We see that convective motions extend beyond the Schwarzschild boundary of the convection zone, which is denoted by a horizontal dashed grey line.
These motions come to a halt at the top of a penetration zone, denoted by a solid horizontal line, where the gradient departs from the adiabatic towards the radiative gradient.
In the right panel, we display temperature perturbations away from the time-evolving mean temperature profile.
We see that warm upwellings in the Schwarzschild-unstable convection zone (below the dashed line) become cold upwellings in the penetration zone (above the dashed line), and these motions excite gravity waves in the stable radiative zone (above the solid line).

We further explore the simulation from Fig.~\ref{fig:vertical_dynamics_panels} in Fig.~\ref{fig:grad_profiles} by displaying time- and horizontally-averaged 1D profiles of the thermodynamic gradient $\justgrad$ (defined in Sec.~\ref{sec:theory}).
The adiabatic gradient $\gradad$ is shown in purple and is a constant value in the simulation.
The radiative gradient $\gradrad$ is shown in orange.
The domain exhibits a classical Schwarzshild-unstable convection zone (CZ) for $z \lesssim 1.04$ where $\gradrad > \gradad$; the upper boundary of this region is denoted by a dashed vertical line.
Above this point, $\gradrad < \gradad$ and the domain would be considered stable by the Schwarzschild criterion.
However, the evolved convective dynamics in Fig.~\ref{fig:vertical_dynamics_panels} have raised $\justgrad \rightarrow \gradad$ in an extended penetration zone (PZ) which extends from roughly $1.04 \leq z \leq 1.4$.
Above this point, $\justgrad$ departs from $\gradad$, returning to $\gradrad$ in a classical stable radiative zone (RZ).

Our goals in this paper are to understand how these PZs form, and to parameterize this effect so that it can be included in 1D stellar evolution calculations.

\newpage
\section{Theory}
\label{sec:theory}

\subsection{Equations \& flux definitions}
\label{sec:theory_equations}
Throughout this work, we will utilize a modified version of the incompressible Boussinesq equations,
\begin{align}
&\grad\dot\vec{u} = 0 
\label{eqn:incompressible} \\
&\partial_t \vec{u} + \vec{u}\dot\grad\vec{u} = -\frac{1}{\rho_0}\grad p + \frac{\rho_1}{\rho_0}\vec{g} + \nu\grad^2 \vec{u} 
\label{eqn:momentum} \\
&\partial_t T + \vec{u}\dot\grad T + w \gradad + \grad\dot[-k \grad \overline{T}] = \chi\grad^2 T' + Q
\label{eqn:temperature} \\
&\frac{\rho_1}{\rho_0} = -|\alpha| T.
\label{eqn:boussinesq}
\end{align}
Here, the density is decomposed into a constant background $\rho_0$ with fluctuations $\rho_1$ which appear only in the buoyancy force and depend on the temperature $T$ and the coefficient of thermal expansion $\alpha = \partial\ln\rho / \partial T$.
We furthermore define the velocity vector $\vec{u}$, the viscous diffusivity $\nu$, the thermal diffusivity $\chi$, the bulk internal heating $Q$, the adiabatic gradient $\gradad$, and a height-dependent thermal conductivity $k$.
We will consider Cartesian coordinates $(x, y, z)$ with a constant vertical gravity $\vec{g} = -g\hat{z}$.
Throughout this work, we will represent horizontal averages with bars ($\overline{\,\cdot\,}$) and fluctuations away from those averages with primes ($'$).
Thus, in Eqn.~\ref{eqn:temperature}, $\bar{T}$ is the horizontally averaged temperature and $T'$ are fluctuations away from that; both of these fields evolve in time according to Eqn.~\ref{eqn:temperature}.

@@

Taking a dot product of the velocity and Eqn.~\ref{eqn:momentum} reveals the kinetic energy equation,
\begin{equation}
\frac{\partial \mathcal{K}}{\partial t}
+ \grad\dot\mathcal{F}
= \mathcal{B} - \Phi,
%\frac{\partial}{\partial t}\left(\frac{|\vec{u}|^2}{2}\right) 
%+ \grad\dot\left[\vec{u}\left(\frac{|\vec{u}|^2}{2} + \frac{p}{\rho_0}\right) - \nu\vec{u}\cross\vec{\omega}\right]
%= |\alpha| g w T - \nu|\vec{\omega}|^2,
\label{eqn:kinetic_energy}
\end{equation}
where we define the kinetic energy $\mathcal{K} \equiv |\vec{u}|^2/2$, the fluxes of kinetic energy $\mathcal{F} \equiv \left[\vec{u}(\mathcal{K} + p/\rho_0) - \nu\vec{u}\cross\vec{\omega} \right]$, the buoyant energy generation rate $\mathcal{B} \equiv |\alpha| g w T'$, and the viscous dissipation rate $\Phi \equiv \nu |\vec{\omega}|^2$ where $\vec{\omega} = \grad\cross\vec{u}$ is the vorticity and $|\vec{u}|^2 = \vec{u}\dot\vec{u}$ \& $|\vec{\omega}|^2 = \vec{\omega}\dot\vec{\omega}$.
We next take a horizontal- and time-average of Eqn.~\ref{eqn:kinetic_energy} (we absorb the time-average into the horizontal-average $\bar{\,\cdot\,}$ notation for simplicity).
Assuming that $\bar{\mathcal{K}}$ reaches a statistically stationary state, convective motions satisfy
\begin{equation}
\frac{d\bar{\mathcal{F}}}{dz} = \bar{\mathcal{B}} - \bar{\Phi}.
\label{eqn:kinetic_energy_1D}
\end{equation}
It is reasonable to assume that $\mathcal{F}$ is zero at the boundaries of the convecting region (see Fig.~\ref{fig:theory_profiles}, upper panel).
We integrate Eqn.~\ref{eqn:kinetic_energy_1D} vertically between these zeros of the flux to find
\begin{equation}
\int \bar{\mathcal{B}}\,dz = \int \bar{\Phi}\,dz.
\label{eqn:integral_constraint}
\end{equation}
Integral constraints of this form are the basis for a broad range of analyses in Boussinesq convection \citep[see e.g.,][]{ahlers_etal_2009, goluskin2016} and were considered in the context of penetrative stellar convection by \citet{roxburgh1989}.
Eqn.~\ref{eqn:integral_constraint} is the straightforward statement that work by buoyancy on large scales must be balanced by viscous dissipation on small scales.

@@

We now find it instructive to break up the convecting region into a Schwarzschild-unstable ``convection zone'' (CZ) and a extended ``penetration zone'' (PZ); we assume that convective motions efficiently mix $\justgrad \rightarrow \gradad$ in both the CZ and PZ.
We note that the buoyant energy generation is proportional to the convective flux, $\bar{\mathcal{B}} = |\alpha|g\bar{w T'} = |\alpha| g \bar{\Fconv}$.
Thus, in the PZ where $\gradad > \gradrad$ (see Fig.~\ref{fig:theory_profiles}, middle panel), we know that $\bar{\Fconv} < 0$ and so $\bar{\mathcal{B}} < 0$ too (see the discussion around Eqn.~\ref{eqn:gradrad_definition}).
Breaking up Eqn.~\ref{eqn:integral_constraint}, we see that
\begin{equation}
%\int_{\rm{CZ}} \bar{\mathcal{B}}\,dz \qquad=\qquad
\int_{\rm{CZ}} \bar{\mathcal{B}}\,dz \,\,=\,\,
\int_{\rm{CZ}} \bar{\Phi}\,dz + \int_{\rm{PZ}} \bar{\Phi}\,dz + \int_{\rm{PZ}}(-\bar{\mathcal{B}})\,dz.
\label{eqn:constraint_cz_pz_split}
\end{equation}
Eqn.~\ref{eqn:constraint_cz_pz_split} is thus arranged so that the (positive) buoyant engine of convection is on the left-hand side, and the (positive) sinks of work are on the RHS.
We see that the size of the PZ is set by some combination of viscous dissipation and buoyancy breaking.
We now parameterize the fraction of the buoyant engine consumed by CZ dissipation  
\begin{equation}
f \equiv \frac{\int_{\rm{CZ}} \bar{\Phi}\,dz}{\int_{\rm{CZ}}\bar{\mathcal{B}}\,dz}.
\label{eqn:f_defn}
\end{equation}
Under this parameterization, Eqn.~\ref{eqn:constraint_cz_pz_split} can be written
\begin{equation}
\frac{\int_{\rm{PZ}}(-\bar{\mathcal{B}})\,dz}{\int_{\rm{CZ}} \bar{\mathcal{B}}\,dz}
+ \frac{\int_{\rm{PZ}} \bar{\Phi}\,dz }{\int_{\rm{CZ}} \bar{\mathcal{B}}\,dz}
= (1 - f),
\label{eqn:first_pz_parameterization}
\end{equation}
and we can immediately read off limits on a hypothetical PZ according to $f$,
\begin{enumerate}
\item Viscous dissipation is inefficient in the limit that $f \rightarrow 0$.
Reasonably also assuming that $\int_{\rm{PZ}}\bar{\Phi}\,dz \rightarrow 0$, Eqn.~\ref{eqn:first_pz_parameterization} states that the PZ must be large enough for its negative buoyant work to be equal in magnitude to the positive buoyant work of the CZ.
This is the integral constraint on the maximum size of the PZ that \citet{roxburgh1989} derived.
\item In the limit that $f \rightarrow 1$, viscous dissipation efficiently counteracts the buoyancy work in the CZ.
Per Eqn.~\ref{eqn:first_pz_parameterization}, the positive-definite PZ terms must approach zero and no PZ develops in this limit.
This is mathematically equivalent to standard boundary-driven convection experiments.
\end{enumerate}
In general, we anticipate from the results of e.g., \citet{currie_browning_2017} that $f$ is closer to 1 than 0, but its precise value must be measured directly from simulations.
Indeed, we find that $f \gg 0$ but $f < 1$ in our simulations (see e.g., Fig.~\ref{fig:theory_profiles}, bottom panel\footnote{the bulk dynamics suggest by eye $f \sim 0.5$, but due to e.g., the height dependence of $\bar{\mathcal{B}}$ in our simulations we measure $f \approx 0.74$.}).

@@

The fundamental result of this theory is Eqn.~\ref{eqn:theory_fraction}, which is a parameterized and generalized form of \citet{roxburgh1989}'s integral constraint.
This equation is also reminiscent of \citet{zahn1991}'s theory, and says that the size of a PZ is set by the profile of $\gradrad$ near the convective boundary (which we quantify in Eqn.~\ref{eqn:theory_P_defn}).
The parameters $f$ and $\xi$ are measurables which can be constrained by direct numerical simulations.
In general, we expect that $f$ and $\xi$ should not change too drastically with other simulation parameters.

@@

In Fig.~\ref{fig:time_evolution}, we show the time evolution of a Case I (discontinuous conductivity) simulation with $\mR = 400$, $\mS = 10^3$, and $\mP_D = 4$ whose initial conditions roughly set $\justgrad = \gradad$ in the convection zone ($z \lesssim 1$) and $\justgrad = \gradrad$ in the radiative zone ($z \gtrsim 1$).
In the top left panel, we display the measured extent of the penetrative region $\delta_{\rm{0.5}}$ vs.~time.
This region initially grows quickly over hundreds of freefall times, but this evolution slows down as the convective dynamics establish themselves and the final equilibration takes tens of thousands of convective overturn (freefall) times.
The evolution of the other parameters in our theory ($f$, $\xi$) are shown in the middle and bottom left panels of Fig.~\ref{fig:time_evolution}.
We plot their rolling mean, averaged over 200 freefall time units. 
We see that the values of $f$ and $\xi$ reach their final values ($f \approx 0.67$, $\xi \approx 0.58$) faster than the penetration zone evolves to its full depth.
We quantify this fast evolution by plotting a vertical line in each of the left three panels corresponding to the first time at which the rolling average converges to within 1\% of its final value (averaged over the final 1000 freefall times of the simulation and plotted as a grey horizontal line).
The evolved value of $f$ indicates that roughly 2/3 of the buoyancy work is dissipated in the bulk CZ, so that 1/3 is available for PZ dissipation and negative buoyancy work.
The evolved value of $\xi$ indicates that the shape of dissipation in the PZ is slightly steeper than linear.

In the right panel of Fig.~\ref{fig:time_evolution}, we display the realized profile of $\justgrad/\gradad$ in our simulations at regular time intervals, where the color of the profiles corresponds to time, as in the left panels.
$\gradad$ is plotted as a dashed horizontal line while $\gradrad$ is plotted as a grey solid line which decreases with height around $z \approx 1$ and satures to a constant above $z \gtrsim 1.1$.
The location of the Schwarzschild boundary, $L_s$, is overplotted as a black vertical dashed line and does not evolve over the course of the simulation.
We note that the Schwarzschild boundary does not move over the course of our simulation, so the extention of the convection zone past this point is true penetration and not the result of entrainment-induced changes in the Schwarzschild (or Ledoux) convective boundaries.
The traces of $\delta_{0.1}$ and $\delta_{0.9}$ are plotted as red lines while that of $\delta_{0.5}$ is plotted as a black line.
We see that the fast initial evolution establishes a sizeable PZ (denoted by purple $\justgrad$ profiles), but its final equilibration slows down (indicated by the separation between the purple, green, and yellow profiles decreasing over time).
%This occurs in part because the flattening of $\justgrad < \gradrad$ above the penetrative zone increases the effective value of $N^2$ and thus the stiffness at the PZ-RZ boundary; however, this long evolution occurs on timescales similar to the thermal diffusion time in the RZ.
